A quantitative framework for investigating the reliability of empirical network construction

### 2019-01-11 manuscript/reply_to_reviewers.tex

		\textbf{R:} This comment echoes the impression of Reviewers 1 (above) and 3 (below) that we do not give adequate attention to previous work. As stated above, we have now added many further pointers to previous work, and also been much more explicit regarding whom we try to reach with what message in the current paper.

	2. Non-independence of interactions not accounted for [done]

		\begin{refquote}
			2/ network oversight: the approach considers that the interactions are independent, which is not the case in real data. Indeed, the paper is supposed to be “network-oriented“ but the methodology deals with independent interactions (e.g. the variables L,T,X and D introduced lines 62,77,101 are for instance not indexed by ij which could have suggested that the interactions were seen as a whole). Consequently, the mathematical framework remains quite simple and may not reflect nor model the processes governing the actual detection of interactions. Despite of this drawback, the proposed method is interesting but at least the authors should add some discussion on the limits of dealing with independent interactions,
		\end{refquote}

		\textbf{R:} We agree wholeheartedly that ecological interactions are often not independent. Indeed, some of the priors we discuss (e.g., those incorporating species' abundances or trait-matching) will introduce covariance between interactions. The Reviewer is correct that we did not initially mention this non-independence explicitly. Our aim is to keep our mathematical framework simple so that it is easy for those not familiar with Bayesian analysis to adopt. Nevertheless, non-independence of interactions is an important consideration. We are therefore happy to index all variables referring to interactions by ij and we have added an explicit statement (lines XX-XX) that some priors treat interactions independently while others will introduce covariance (e.g., by species).

		Lines XX-XX:

		\begin{quotation}
		    The shape parameters, or hyperparameters, may be set to particular values or derived from some data (see below). Note that the hyperparameters may be set to the same values for all interactions, allowed to vary independently for all interactions, or may incorporate non-independence betwween interactions (e.g., when the shape of the prior distribution depends upon species' abundances or traits).
		\end{quotation}

	3. Question about identifiability of the model [done]

			the reader would appreciate that the authors discuss and prove the identifiability of the model. Indeed, the three levels of uncertainity are nested but one could wonder whether different parameters at the three levels can fit the same data with the same quality (i.e. no identifiability).  I would suggest this point to be addressed in a specific section.

@@

			the reader would appreciate that the authors discuss and prove the identifiability of the model. Indeed, the three levels of uncertainity are nested but one could wonder whether different parameters at the three levels can fit the same data with the same quality (i.e. no identifiability).  I would suggest this point to be addressed in a specific section.

		\end{refquote}

		\textbf{R:} We believe that this comment stems from a lack of clarity about the goal of our model. It is not designed to separate the three levels of uncertainty or introduce parameters at particular levels. The only inputs are a prior distribution, which could refer to any level of uncertainty applicable to the study at hand, and post-hoc counts of interactions and co-occurrences. Using only the observed data, it is impossible to separate the three levels of uncertainty and our model does not aim to do so (as stated in lines XX-XX and lines XX-XX). We therefore do not believe that an in-depth discussion of identifiability would add much value to the manuscript and, in the interest of space, have decided not to include one.

		Lines XX-XX:

		\begin{quotation}
			When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij} = 0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.~\ref{conceptual_fig}). Unfortunately, this is not possible for most interactions (except those where we know an interaction is truly not feasible). That is, we generally do not know \emph{why} an interaction was not observed, only that it was not. An empirical ecologist will instead measure the marginal probability $P(L_{ij}) = k_{ij}/n_{ij}$, where $k_{ij}$ is the number of observed interactions between species $i$ and $j$ and $n_{ij}$ the number of observed co-occurrences. Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?
		\end{quotation}

		Lines XX-XX:

		\begin{quotation}
			Note that these Bayesian models of $\lambda_{ij}$ are designed to quantify (and reduce) the total uncertainty about $\lambda_{ij}$. They do not address any of the nested sources of uncertainty in particular except through the choice of prior.
		\end{quotation}

	4. Request for a simulation study [done; thanks Tomas]

		\begin{refquote}
			the authors proposed an original approach based on a bayesian framework. Beyond the identifiability question (see above), the reader can question the power of the method. Usually, a methodological proposal comes with a complete simulation study that is supposed to show  the proposed model is adapted/suitable to the question and efficient to solve it. In the paper in its present form, the authors assume that the reader will be convinced by the results obtained on a single real dataset… In my opinion, the reader can’t be fairly convinced: how powerfull is the method? what can we say about the priors? how much data (n, k) is necessary to expect good results? An so on… Only a well-conducted simulation study can answer these questions.
		\end{refquote}

		\textbf{R:} We agree with the Reviewer that a full simulation study, based on recreating the sources of uncertainty in a data set generated from known processes, is an excellent way to demonstrate the power of a novel method. The novelty and impact of our work, however, is not in the method itself (several other Reviewers rightly point out that similar approaches have occasionally been used before) but in connecting a Bayesian statistical approach to the problem of limited and uneven sampling of networks and, we hope, in making this method more accessible to those without extensive statistical or modelling experience. In other words, what we try to achieve here is to alert empirical ecologists constructing and analyzing networks to the uncertainties built into their work. We then try to provide them with simple tools for grasping the extent and consequences of typical patterns. Please note that other Reviewers (as expressed by Reviewer 3 in particular) find this a highly worthwhile objective.

		What Reviewer 2 proposes would be more suitable for an entirely novel method and is substantially beyond the scope of the present study. There is indubitably a place for simulation studies in order to find the most powerful method once a variety of tools are in common use, especially for researchers aiming to convince modellers that their tool is more powerful. Our manuscript, however, is not aimed at those already comfortable with Bayesian approaches but rather at those who may be aware of the problems of uneven uncertainty but not aware of any way to include this information in their analyses. We are confident that even a very simple model which incorporates the differences in sampling across interactions (as ours does) is more powerful than a model which ignores this information completely, and we therefore do not intend to conduct a full-scale simulation study. We accept that this means that those already using more intricate Bayesian methods are unlikely to switch to our simpler version; it was never our intention that they should do so.

	5. Request for an extended results and discussion section [no actual response, just words]

		\begin{refquote}
			5/ results\&discussion too short: the reader is surprised to read 27 lines of raw results only… Given the amount of new methodology that is proposed, one can expect a complete description of its pros and cons. Obvisouly, a simulation study (see above) would enrich the results part. Forgetting about the length of these parts, it is still difficult to catch the key messages from the text, and it is not obvious to relate discussion and the obtained results (for instance,from l.343 to l.351).
		\end{refquote}

		\textbf{R:} We very much appreciate the Reviewer's point that the results and discussion do not clearly illustrate the point of the manuscript. Although we have not conducted a simulation study (see above), we have extensively revised these sections in order to highlight the main thread through the manuscript. Due to space limitations, we were unable to greatly expand either section (we prioritise the introduciton and methods, which lay out the problem of uncertainty in networks and how it can be partially addressed), but we hope that the results now more clearly demonstrate how a Bayesian approach can address the uncertainty inherent in sampling.

	6. Suggestions to improve notation [done? unless anyone else can figure out the last part...]

	\begin{refquote}
		6/ lack of rigorous notations: it is possible to understand the approach with the present notations but some improvements can help the reader because there are a series of inconsistencies. Here are some suggestions. The authors chose upper case letters L,T ,X,D for single entities whereas the mathematician is used to expect matrices or constants in upper case. Traditionaly, given species i and j, we would consider interaction $L_ij$, feasibility $X_ij$, detectionability $D_ij$... \\
		Still, what is T?? not defined, never reused: is it a characteristics on i, on j, on both? \\
		How can be D<1 on l.169? D=0 or 1 since it says if an interaction is detectable or not... \\
		Moreover, L is reused later but is the number of interactions (l.100 supp.mat)… \\
		What is “N” in Figure 4? is it “n”? What is $n_ij$ and $k_ij$ l.266? Never defined, never reused. \\
		In the beginning of the paper, $\lambda$ is a probability (l.62) but it becomes a random variable (l.164): it would be more consistent to introduce before the notion of hyperparameters  (l.209-213) and to explain we consider that $\lambda$ is drawn into its distribution.
	\end{refquote}

	\textbf{R:} 
		\begin{itemize}
			\item As described above, we have now indexed $L$, $T$, $X$, $D$, etc. by $ij$. 
			\item $T$ describes trait matching, so it is a characterisation on $i$ and $j$ together. 
			\item $D$ can be \textless1 because some interactions are detectable but with a lower probability due to limitations in sampling techniques, sampling time, etc. With infinite monitoring time and capacity, all $D_{ij}$ would indeed be 0 or 1, but given real-world constraints that lead to otherwise-detectable interactions being missed, we feel it makes sense to discuss $0<D_{ij}<1$. For instance, consider a predator feeding upon two prey. If one of the prey (A) has many hard parts and is digested slowly, while the other has no hard parts and is digested quickly (B), the interaction involving prey A will be more detectable than the interaction involving prey B. The interaction with prey B is does not have D=0, because the interaction might be observed directly or through examination of gut contents very soon after B was consumed, but we cannot say that D=1 because we are quite likely not to detect this interaction in any given sample.
			\item Using L to mean the number of interactions is incredibly common in the food-web literature, especially when defining connectance (as in the instance the Reviewer points out - now included in the main text). That said, we appreciate that this useage may confuse mathematicians. We therefore now define the number of interactions as N and hope that this is less puzzling.
			\item Yes, the N on figure 4 should have been $n_{ij}$. This has been corrected. As discussed above, $n$ and $k$ are now always indexed by $ij$. 
			\item We do not catch what the Reviewer is aiming at here. We hope that our revised introduction and methods have addressed this point; if not, we request that the Reviewer kindly provide some more detail so that we can address his/her concern.

### 2019-01-11 manuscript/CI_interactions.tex
almost finished addressing R2

          First, and most fundamentally, some interactions are feasible if a pair of species should co-occur while others are not~\citep{Poisot2015}. Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L$ given some description of trait-matching $\mathbf{T}$ as $P(L|\mathbf{T}) = \lambda$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}. 
          In some cases the traits prohibiting an interaction are known, and there will be little uncertainty about $\lambda$.
          In most cases, however, it is not known what traits might prohibit an interaction~\citep{Dormann2017}. Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{Weinstein2017a} and herbivores may consume animal prey when it becomes accessible~\citep{Furness1988,Pietz2000}. These examples illustrate the danger in assuming that seemingly unlikely interactions cannot occur.

          An unobserved interaction may be a rare phenomenon with $\lambda>0$ and the associated zero in an interaction matrix might be false. This uncertainty is partly addressed by trait-matching models in which species with better-matched traits are more likely to interact~\citep{Bartomeus2016,Jordano2016,Weinstein2017}. As these models improve and include better information about the influence of traits on interactions, the uncertainty will be reduced~\citep{Jordano2016} and $\lambda$ should either tend to 0 or to 1. Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}. Until these gaps are filled, some uncertainty will remain about whether some species pairs could interact.

@@

          Assuming that an interaction is feasible (i.e., $L=1$;), an interaction may still not occur at a particular place or time~\citep{Poisot2015,Graham2018}. This could be because constraints such as inclement weather or low abundance prevented the interaction~\citep{Jordano2016,Graham2018}, a more preferred interaction partner was available~\citep{Weinstein2017a}, or substantial individual variation in traits meant that local individuals could not interact even if the species in general can~\citep{Gravel2013,Wells2013,Poisot2015}. For example, a rare galler may not parasitize a rare plant because they do not encounter each other. In metawebs describing a community found at several sites, an interaction may also fail to occur because two species do not co-occur at a particular site even if they do co-occur and interact elsewhere~\citep{Graham2018}. We can define the local realisation of an interaction, $X$, given that the interaction is feasible, as a stochastic process with associated probability $P(X|L=1)=\chi$. It is unlikely that $\chi=1$  except in the case of obligate specialists who always interact whenever they co-occur and always co-occur. When $\chi<1$ we cannot be sure whether an unobserved interaction cannot occur or whether it simply did not occur at a particular site.

          Some of the uncertainty about $\chi$ could be addressed by drawing on the rich literature about interaction contingencies found in community ecology. Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects~\citep{Luttbeg2005,Wirsing2008} all affect the probability of an interaction occurring at a particular site and time, and could be included in models similar to trait-matching models. Alternatively, interaction probabilities could be tested in mesocosm studies with constant conditions. Some studies attempt to reduce uncertainty by sampling intensively over a short period of time and restricting the scale of interest to interactions occurring at the sampling site and time (conflating $\chi$ and $\lambda$)~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a}. This approach may be suitable for some research questions, but is not appropriate if we wish to assemble the full set of interactions which occur in a community (beyond the specific site and time of sampling). In contrast, expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of microhabitats or during a variety of weather conditions) will help to reduce uncertainty about $\chi$ by including a broader range of parameters affecting interaction probability. It is unlikely, however, that resources will permit researchers to sample in the full range of sites and conditions covered by a community, and some uncertainty about $\chi$ will remain.

@@

            Both whether species can interact and whether they do interact at a particular place and time have been discussed in the context of "forbidden links"~\citep{Jordano2016}. In this framework, all links which are prevented by spatio-temporal uncoupling, physiological constraints, etc. are considered "structural zeros" that cannot be observed~\citep{Jordano1987,Jordano2016}. We conceptually distinguish between physiological constraints and spatio-temporal uncoupling to allow for cases in which a species is introduced to a new habitat, expands its range, or shifts phenology~\citep{Gravel2013}. In such cases, links which are forbidden due to physiological constraints remain forbidden but links previously forbidden due to spatio-temporal mismatch could potentially occur.

@@

          Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes. Even if an interaction is feasible and occurs during sampling ($L = 1$ and $X = 1$), we may still fail to detect it~\citep{Jordano2016,Weinstein2017}. We may define the probability of detecting of an interaction, $D$, given the interaction is feasible and occurs, as a stochastic process with the associated probability $P(D|X=1,L=1)=\delta$. Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples and partial solutions to them). Some sources of detection error can be minimised with appropriate sampling effort (e.g., combining plant-focused and animal-focused sampling when assembling pollination networks~\citet{Jordano2016}), but other sources are often difficult to reduce. For example, cryptic species might require molecular analysis for appropriate taxonomic identification~\citep{Wirta2014,Frost2016} or it may not be possible to sample some species due to conservation concerns~\citep{Lagrue2015}.

@@

        To sum up, the absence of an interaction on a given day could  be because it was not feasible [$P(L) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X|L=1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D|X=1,L=1)=0$]. Note that some exteral factors can affect more than one level of uncertainty. For example, rare species are less likely to interact at a given site due to neutral processes~\citep{Jordano2016,Graham2018}. Interactions involving rare species are also less likely to be detected, unless more sampling effort is focused on rare than common species~\citep{Bartomeus2013,Jordano2016}. Thus, abundance affects both the probability of an interaction occurring at a particular site \emph{and} our ability to observe the interaction.

        When considering a metaweb, we wish to separate the unobserved interactions where $L = 0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.~\ref{conceptual_fig}). Unfortunately, this is not possible for most interactions (except those where we know an interaction is truly not feasible). An empirical ecologist will instead measure the marginal probability $P(L) = k/n$, where $k$ is the number of observed interactions and $n$ the number of observed co-occurrences. Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?

        The obvious rule of thumb to reduce uncertainty is ``sample more". Where resources permit, increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L$=1 but process or detection uncertainty is high). Despite these benefits, we note that there are limits to the utility of increased sampling. Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}C). While this improves our understanding of the set of species present in the community, it introduces yet more uncertainty into the interaction matrix. Note that it is better to identify the set of potential interactions than to miss a species, so sampling effort should not be reduced in order to exclude rare species.

        An added complication is that increased sampling will not reduce uncertainty evenly across interactions. To record an interaction between A and B, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citealp{Kaartinen2011,Roslin2016}). For both molecular and rearing techniques, certain types of interactions may go unnoticed due to technical challenges~\citep{Wirta2014}. This can bias the set of recorded interactions towards those that are easier to observe~\citep{Carstensen2014,Jordano2016}. Combining multiple sampling types can reduce this type of bias~\citep{Wirta2014,Jordano2016}. Nevertheless, despite substantial improvements in recent decades, most available interaction networks are still undersampled and, moreover, are only subsets of larger communities~\citep{Bartomeus2013,Jordano2016}.

@@

    % Assume that a pair of species has been observed co-occurring $n$ times and interacting in $k = 0$ cases. We want to know the probability $\lambda$ that the species would be observed interacting if not constrained by local conditions, imperfect detection, etc. We can consider the occurrence of an interaction as a Bernoulli trail where the number of successes ($k$) over $n$ trials will follow a binomial distribution (see~\emph{Appendix S2} for a full description of the mathematical framework). In this framework, the maximum likelihood estimate (MLE) for $\lambda$ is:

@@

    % Note that $\lambda$ is not a point estimate but rather a random variable with an unknown distribution. This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact. Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact. In the situation where $k>0$, in contrast, we are sure that the interaction is feasible ($L = 1$). If $n>k>0$, the interaction is feasible but there may be local constraints ($X = 0$) or detection errors ($D<1$) causing the interaction not to be observed in some samples.

    % To properly interpret $\lambda$, we need to estimate the variance as well as the MLE. The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda$) and, importantly, describes the variability of the number of successes $k$ for $n$ trials rather than the variance associated with the estimation of $\lambda$. It is, however, straightforward to compute the confidence interval for the MLE of $\lambda$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]).

    % All of the above methods for estimating the variance of $\lambda$ include the number of samples $n$. This means that where the number of samples $n$ is very low (e.g., for rare species), there will be considerable uncertainty around our estimate of $\lambda$. In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda$ (for true $\lambda = 0$) varies with sample size. At a small sample size, the 95\% confidence interval is nearly (0, 1). To establish that species are not interacting with any acceptable certainty requires tens of observations of the two species co-occurring but not interacting. Most data sets will lack such extensive sampling across all species pairs, but we can still use a Bayesian approach to supplement the available data with other sources of information.

    The basis of a Bayesian approach to modelling the probability that an interaction occurs ($\lambda$) is combining the maximum likelihood estimate (MLE) of $\lambda$ with a prior distribution (described in the next section) and a normalising function. The MLE of $\lambda$ can be modelled as a Bernoulli trial based on the number of observed interactions $k$ and observed co-occurrances $n$: $\lambda = \frac{k}{n}$. The most appropriate prior distribution for a probability such as $\lambda$ is the beta distribution:

    \begin{equation}
          \lambda \sim Beta(\alpha,\beta) , \label{prior}
        \end{equation}

        \noindent which has two shape parameters, $\alpha$ and $\beta$.

    The shape parameters, or hyperparameters, may be set to particular values or derived from some data (see below). Combining the prior distribution with the MLE of $\lambda$ derived from observed data, we obtain a posterior distribution that also follows a beta distribution with new parameters $\alpha'= \alpha+k$ and $\beta'=\beta+n-k$ (see~\emph{Appendix S2} for details). The influence of the prior on the posterior distribution can be understood from these parameter definitions: the difference between the posterior and the prior will increase with $k$ and $n-k$. In other words, the distribution of $\lambda$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and depend more on the observed data and uncertainty about the probability of the pair interacting will decrease (Fig.~\ref{Salix_pdfs_cdfs}).

@@

    %   It is common to perform analyses that require calculating higher-order network properties in interaction networks. The fact that the posterior distribution of $\lambda$ follows a beta distribution makes it straightforward to compute moments and other properties needed for these analyses.

    %   The \textbf{average} of $\lambda$ is: 
    %       \begin{equation}
    %         \bar{\lambda} = \frac{\alpha+k}{\alpha+\beta+n} ,
    %         \label{mean}
    %       \end{equation}

    %     and its \textbf{variance} is:  
    %       \begin{equation}
    %         Var(\lambda|k) = \frac{(\alpha + k)(\beta + n - k)}{(\alpha + \beta + n)^{2}(\alpha + \beta + n +1)}
    %         \label{variance}
    %       \end{equation}

    %     The \textbf{mode} of the distribution is:
    %       \begin{equation}
    %         \hat{\lambda} = \frac{\alpha + k - 1}{\alpha + \beta + n - 2} .
    %         \label{mode}
    %       \end{equation}

>>>>

          First, and most fundamentally, some interactions are feasible if a pair of species should co-occur while others are not~\citep{Poisot2015}. Assuming that the feasibility of interactions depends on the traits of species involved, we can define the probability of an interaction $L_{ij}$ between species $i$ and $j$, given some description of trait-matching $\mathbf{T_{ij}}$, as $P(L_{ij}|\mathbf{T_{ij}}) = \lambda_{ij}$~\citep{Bartomeus2013,Gravel2013,Weinstein2017}. 
          In some cases the traits prohibiting an interaction are known, and there will be little uncertainty about $\lambda_{ij}$.
          In most cases, however, it is not known what traits might prohibit an interaction~\citep{Dormann2017}. Pollinators may visit plants outside of those predicted based on "pollination syndromes"~\citep{Weinstein2017a} and herbivores may consume animal prey when it becomes accessible~\citep{Furness1988,Pietz2000}. These examples illustrate the danger in assuming that seemingly unlikely interactions cannot occur.

          An unobserved interaction may be a rare phenomenon with $\lambda>0$ and the associated zero in an interaction matrix might be false. This uncertainty is partly addressed by trait-matching models in which species with better-matched traits are more likely to interact~\citep{Bartomeus2016,Jordano2016,Weinstein2017}. As these models improve and include better information about the influence of traits on interactions, the uncertainty will be reduced~\citep{Jordano2016} and $\lambda_{ij}$ should either tend to 0 or to 1. Nevertheless, every model is imperfect and lacks information that could be used to define constraints on at least some interactions~\citep{Dormann2017}. Until these gaps are filled, some uncertainty will remain about whether some species pairs could interact.

@@

          Assuming that an interaction is feasible (i.e., $L_{ij} = 1$;), an interaction may still not occur at a particular place or time~\citep{Poisot2015,Graham2018}. This could be because constraints such as inclement weather or low abundance prevented the interaction~\citep{Jordano2016,Graham2018}, a more preferred interaction partner was available~\citep{Weinstein2017a}, or substantial individual variation in traits meant that local individuals could not interact even if the species in general can~\citep{Gravel2013,Wells2013,Poisot2015}. For example, a rare galler may not parasitize a rare plant because they do not encounter each other. In metawebs describing a community found at several sites, an interaction may also fail to occur because two species do not co-occur at a particular site even if they do co-occur and interact elsewhere~\citep{Graham2018}. We can define the local realisation of an interaction, $X_{ij}$, given that the interaction is feasible, as a stochastic process with associated probability $P(X_{ij}|L_{ij} = 1) = \chi_{ij}$. It is unlikely that $\chi_{ij} = 1$  except in the case of obligate specialists who always interact whenever they co-occur and always co-occur. When $\chi_{ij} < 1$ we cannot be sure whether an unobserved interaction cannot occur or whether it simply did not occur at a particular site.

          Some of the uncertainty about $\chi_{ij}$$ could be addressed by drawing on the rich literature about interaction contingencies found in community ecology. Phenological matching~\citep{MillerRushing2010,Gezon2016}, species preferences~\citep{Pires2011,Novak2015,Coux2016}, and fear effects~\citep{Luttbeg2005,Wirsing2008} all affect the probability of an interaction occurring at a particular site and time, and could be included in models similar to trait-matching models. Alternatively, interaction probabilities could be tested in mesocosm studies with constant conditions. Some studies attempt to reduce uncertainty by sampling intensively over a short period of time and restricting the scale of interest to interactions occurring at the sampling site and time (conflating $\chi_{ij}$ and $\lambda_{ij}$)~\citep{Bartomeus2013,Weinstein2017,Weinstein2017a}. This approach may be suitable for some research questions, but is not appropriate if we wish to assemble the full set of interactions which occur in a community (beyond the specific site and time of sampling). In contrast, expanding sampling to cover a broader spatial or temporal range (e.g., sampling in a variety of microhabitats or during a variety of weather conditions) will help to reduce uncertainty about $\chi_{ij}$ by including a broader range of parameters affecting interaction probability. It is unlikely, however, that resources will permit researchers to sample in the full range of sites and conditions covered by a community, and some uncertainty about $\chi_{ij}$ will remain.

@@

            Both whether species can interact and whether they do interact at a particular place and time have been discussed in the context of ``forbidden links"~\citep{Jordano2016}. In this framework, all links which are prevented by spatio-temporal uncoupling, physiological constraints, etc. are considered "structural zeros" that cannot be observed~\citep{Jordano1987,Jordano2016}. We conceptually distinguish between physiological constraints and spatio-temporal uncoupling to allow for cases in which a species is introduced to a new habitat, expands its range, or shifts phenology~\citep{Gravel2013}. In such cases, links which are forbidden due to physiological constraints remain forbidden but links previously forbidden due to spatio-temporal mismatch could potentially occur.

@@

          Lastly, measurement errors are a pervasive source of uncertainty in the observation of ecological processes. Even if an interaction is feasible and occurs during sampling ($L_{ij} = 1$ and $X_{ij} = 1$), we may still fail to detect it~\citep{Jordano2016,Weinstein2017}. We may define the probability of detecting of an interaction, $D_{ij}$, given the interaction is feasible and occurs, as a stochastic process with the associated probability $P(D_{ij}|X_{ij} = 1,L_{ij} = 1)=\delta_{ij}$. Detection failure could happen for many reasons (see~\citet{Wirta2014} for examples and partial solutions to them). Some sources of detection error can be minimised with appropriate sampling effort (e.g., combining plant-focused and animal-focused sampling when assembling pollination networks~\citet{Jordano2016}), but other sources are often difficult to reduce. For example, cryptic species might require molecular analysis for appropriate taxonomic identification~\citep{Wirta2014,Frost2016} or it may not be possible to sample some species due to conservation concerns~\citep{Lagrue2015}.

@@

        To sum up, the absence of an interaction on a given day could  be because it was not feasible [$P(L_{ij}) = 0$], was feasible but did not occur because of local conditions during sampling ($P(X_{ij}|L_{ij} = 1) = 0$], or was feasible and occurred during sampling but could not be observed [$P(D_{ij}|X_{ij} = 1,L_{ij} = 1) = 0$]. Note that some exteral factors can affect more than one level of uncertainty. For example, rare species are less likely to interact at a given site due to neutral processes~\citep{Jordano2016,Graham2018}. Interactions involving rare species are also less likely to be detected, unless more sampling effort is focused on rare than common species~\citep{Bartomeus2013,Jordano2016}. Thus, abundance affects both the probability of an interaction occurring at a particular site \emph{and} our ability to observe the interaction.

        When considering a metaweb, we wish to separate the unobserved interactions where $L_{ij} = 0$ (i.e., unfeasible interactions) from interactions which could occur but did not at a particular sampling site or which occurred but were not detected (Fig.~\ref{conceptual_fig}). Unfortunately, this is not possible for most interactions (except those where we know an interaction is truly not feasible). That is, we generally do not know \emph{why} an interaction was not observed, only that it was not. An empirical ecologist will instead measure the marginal probability $P(L_{ij}) = k_{ij}/n_{ij}$, where $k_{ij}$ is the number of observed interactions between species $i$ and $j$ and $n_{ij}$ the number of observed co-occurrences. Given this information, the question becomes: how can we reduce the uncertainty around our estimated interaction probability?

        The obvious rule of thumb to reduce uncertainty is ``sample more". Where resources permit, increasing sample sizes will reduce uncertainty about the upper bound of the interaction probability and will also increase the probability of detecting unlikely or cryptic interactions (e.g., interactions where $L_{ij} = 1$ but process or detection uncertainty is high). Despite these benefits, we note that there are limits to the utility of increased sampling. Since the probability of observing the co-occurrence of two species will always be higher than the probability of observing their interaction (since the probability of interaction is conditional on both interaction partners being present), we will accumulate observations of co-occurrences faster than we will accumulate observations of interactions (Fig.~\ref{histograms}C). While this improves our understanding of the set of species present in the community, it introduces yet more uncertainty into the interaction matrix. Note that it is better to identify the set of potential interactions than to miss a species, so sampling effort should not be reduced in order to exclude rare species.

        An added complication is that increased sampling will not reduce uncertainty evenly across interactions. To record an interaction between species $i$ and $j$, we need to identify both partners correctly (a non-trivial problem in many food webs; e.g.~\citealp{Kaartinen2011,Roslin2016}). For both molecular and rearing techniques, certain types of interactions may go unnoticed due to technical challenges~\citep{Wirta2014}. This can bias the set of recorded interactions towards those that are easier to observe~\citep{Carstensen2014,Jordano2016}. Combining multiple sampling types can reduce this type of bias~\citep{Wirta2014,Jordano2016}. Nevertheless, despite substantial improvements in recent decades, most available interaction networks are still undersampled and, moreover, are only subsets of larger communities~\citep{Bartomeus2013,Jordano2016}.

@@

    % Assume that a pair of species has been observed co-occurring $n$ times and interacting in $k = 0$ cases. We want to know the probability $\lambda_{ij}$ that the species would be observed interacting if not constrained by local conditions, imperfect detection, etc. We can consider the occurrence of an interaction as a Bernoulli trail where the number of successes ($k$) over $n$ trials will follow a binomial distribution (see~\emph{Appendix S2} for a full description of the mathematical framework). In this framework, the maximum likelihood estimate (MLE) for $\lambda_{ij}$ is:

@@

    % Note that $\lambda_{ij}$ is not a point estimate but rather a random variable with an unknown distribution. This means that if $k = 0$ in a given sample, this does not necessarily imply that the two species will never interact. Rather, $k = 0$ implies that `no interaction' is the most likely outcome when the species do co-occur but there is nonetheless some chance that the two species \emph{could} interact. In the situation where $k>0$, in contrast, we are sure that the interaction is feasible ($L = 1$). If $n>k>0$, the interaction is feasible but there may be local constraints ($X_{ij} = 0$) or detection errors ($D<1$) causing the interaction not to be observed in some samples.

    % To properly interpret $\lambda_{ij}$, we need to estimate the variance as well as the MLE. The variance of a Bernoulli experiment is $n\lambda$(1-$\lambda_{ij}$) and, importantly, describes the variability of the number of successes $k$ for $n$ trials rather than the variance associated with the estimation of $\lambda_{ij}$. It is, however, straightforward to compute the confidence interval for the MLE of $\lambda_{ij}$ using any of several methods, including the \emph{Wilson score interval}, the \emph{Clopper-Pearson interval}, and the \emph{Agresti-Coull interval} (for details, see [\citealp{Brown2001}]).

    % All of the above methods for estimating the variance of $\lambda_{ij}$ include the number of samples $n$. This means that where the number of samples $n$ is very low (e.g., for rare species), there will be considerable uncertainty around our estimate of $\lambda_{ij}$. In Fig.~\ref{upper_limits}, we derive the Clopper-Pearson interval to explore how the estimate of $\lambda_{ij}$ (for true $\lambda = 0$) varies with sample size. At a small sample size, the 95\% confidence interval is nearly (0, 1). To establish that species are not interacting with any acceptable certainty requires tens of observations of the two species co-occurring but not interacting. Most data sets will lack such extensive sampling across all species pairs, but we can still use a Bayesian approach to supplement the available data with other sources of information.

    The basis of a Bayesian approach to modelling the probability that an interaction between species $i$ and $j$ occurs ($\lambda_{ij}$) is combining the maximum likelihood estimate (MLE) of $\lambda_{ij}$ with a prior distribution (described in the next section) and a normalising function. The MLE of $\lambda_{ij}$ can be modelled as a Bernoulli trial based on the number of observed interactions $k_ij$ and observed co-occurrances $n_{ij}$: $\lambda_{ij} = \frac{k_{ij}}{n_{ij}}$. The most appropriate prior distribution for a probability such as $\lambda_{ij}$ is the beta distribution:

    \begin{equation}
          \lambda_{ij} \sim Beta(\alpha_{ij},\beta_{ij}) , \label{prior}
        \end{equation}

        \noindent which has two shape parameters, $\alpha_{ij}$ and $\beta_{ij}$.

    The shape parameters, or hyperparameters, may be set to particular values or derived from some data (see below). Note that the hyperparameters may be set to the same values for all interactions, allowed to vary independently for all interactions, or may incorporate non-independence betwween interactions (e.g., when the shape of the prior distribution depends upon species' abundances or traits).
    Combining the prior distribution with the MLE of $\lambda_{ij}$ derived from observed data, we obtain a posterior distribution that also follows a beta distribution with new parameters $\alpha_{ij}'= \alpha_{ij}+k$ and $\beta_{ij}'=\beta_{ij}+n-k$ (see~\emph{Appendix S2} for details). The influence of the prior on the posterior distribution can be understood from these parameter definitions: the difference between the posterior and the prior will increase with $k_{ij}$ and $n_{ij}-k_{ij}$. In other words, the distribution of $\lambda_{ij}$ for better-sampled pairs of species will rely less on the information used to build the prior distribution and depend more on the observed data and uncertainty about the probability of the pair interacting will decrease (Fig.~\ref{Salix_pdfs_cdfs}). Note that these Bayesian models of $\lambda_{ij}$ are designed to quantify (and reduce) the total uncertainty about $\lambda_{ij}$. They do not address any of the nested sources of uncertainty in particular except through the choice of prior.

@@

    %   It is common to perform analyses that require calculating higher-order network properties in interaction networks. The fact that the posterior distribution of $\lambda_{ij}$ follows a beta distribution makes it straightforward to compute moments and other properties needed for these analyses.

    %   The \textbf{average} of $\lambda_{ij}$ is: 
    %       \begin{equation}
    %         \bar{\lambda} = \frac{\alpha_{ij}+k}{\alpha_{ij}+\beta_{ij}+n} ,
    %         \label{mean}
    %       \end{equation}

    %     and its \textbf{variance} is:  
    %       \begin{equation}
    %         Var(\lambda|k) = \frac{(\alpha_{ij} + k)(\beta_{ij} + n - k)}{(\alpha_{ij} + \beta_{ij} + n)^{2}(\alpha_{ij} + \beta_{ij} + n +1)}
    %         \label{variance}
    %       \end{equation}
